\section{Company Overview}
wrkin.app is an innovative startup headquartered in Bangalore, India, poised to revolutionize the workplace collaboration and HR management landscape. The company's vision is to create a unified digital ecosystem that seamlessly integrates real-time communication, task management, and a comprehensive Human Resource Management System (HRMS). In a market saturated with disconnected tools, wrkin.app aims to provide a single, mobile-first platform that addresses the core needs of modern businesses, particularly Small and Medium Businesses (SMBs). The company is currently in a pre-launch phase, with a small, agile team focused on rapid development and product refinement.

\section{Internship Context}
This report outlines the work and learning undertaken during a 2.5-month Full Stack Android Developer internship at wrkin.app, from May 5, 2025, to July 15, 2025. The internship was an immersive experience in a fast-paced startup environment, offering the opportunity to contribute to a greenfield project with a modern technology stack. The primary focus of the internship was the development of the wrkin.app mobile application, using Flutter for the frontend and Django for the backend.

\section{Significance of the Role}
The Full Stack Android Developer Intern role was a critical position within the development team. The intern was entrusted with significant responsibilities, including the development of core application modules, backend API integration, and participation in the entire software development lifecycle. This role was integral to accelerating the product's time-to-market and ensuring a high-quality user experience. The contributions made during this internship have had a direct and tangible impact on the wrkin.app platform.

\section{Report Structure}
This report is structured to provide a comprehensive overview of the internship experience.
\begin{itemize}
    \item \textbf{Chapter 1: Introduction} provides an overview of the company, the internship context, and the significance of the role.
    \item \textbf{Chapter 2: Objectives and Industry Context Analysis} details the technical, product, and professional objectives of the internship, along with an in-depth analysis of the market and competitive landscape.
    \item \textbf{Chapter 3: Responsibilities} outlines the technical architecture and the specific roles and responsibilities undertaken during the internship.
    \item \textbf{Chapter 4: Result} presents the key achievements, project contributions, and technical challenges overcome.
    \item \textbf{Chapter 5: Conclusion} summarizes the skills developed, performance metrics, and overall learning outcomes.
    \item \textbf{Chapter 6: Literature Overview} provides a future outlook, including product recommendations, and career reflections.
    \item \textbf{Chapter 7: Requirement Engineering} offers a final assessment of the internship and its impact.
\end{itemize}